Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-08 thesis/paper.tex
review analysis

\subsection{Data Analysis} \label{data_analysis}
%Intro and summary
The data analysis was conducted in two major phases \cite{andersson2007spiral}. During the first phase, a hypothesis generating approach \cite{seaman1999qualitative} was used to be able to fulfil the exploratory goal of the study. It was during this phase that the analysis of the API code and documentation was carried out. The second phase included analysis of the interviews, the goal of which was to confirm the hypotheses \cite{seaman1999qualitative} that were formulated in the first phase. Both phases were performed iteratively, together with the data collection. This created the opportunity to improve the process of analysis as the study progressed, as well as allowing the study to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase \cite{andersson2007spiral}.

%Grounded Theory
The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.

%Codes
Each change identified in the spreadsheet was coded based on what module the change occurred in and two other characteristics: a) if the change added, removed or modified functionality, or b) if the change was a cosmetic change.
%Concepts
Grouping the codes by module allowed us to form general concepts of change. However, changes that affected the whole API were categorised on their own.
%Categories
These concepts were then grouped into categories based on common patterns between the concepts.
%Theory
These categories were then used to identify the most interesting trends in the evolution of the API. These trends were later used as a discussion point during the interview.

%RQ1
%We have all the changes and our suggested theories. Categorise them now
The categories identified previously were then coded according to the software maintenance categories \cite{chapin2001types}. The process used followed the decision tree for types \cite{chapin2001types}. Each of the previously identified categories was given a main category of maintenance and a subcategory if appropriate. This was then used to answer \textbf{RQ1}.

Our ability to correctly predict the motives compared to the actual motives of the designers which were made clear during the interviews, will serve as the basis for answering \textbf{RQ1.1}.

@@

%Lehman's - RQ2
The analysis of both the trends and the changes, combined with information gathered during the interview allowed us to answer \textbf{RQ2} by determining if Lehman's laws are applicable to APIs \cite{lehman1980programs}.

%RQ1.1
The final stage of analysis was conducted once all the data had been analysed. To answer \textbf{RQ1.1}, we compared our analysis and interpretation of the change intents against the opinions expressed during the interview. Success was determined based on the amount of correct interpretations made about the intent behind the changes.

>>>>

\subsection{Data Analysis} \label{data_analysis}
%Intro and summary
The data analysis was conducted in two major phases \cite{andersson2007spiral}. During the first phase, a hypothesis generating approach \cite{seaman1999qualitative} was used to be able to fulfil the exploratory goal of the study. It was during this phase that the analysis of the API code and documentation was carried out. The second phase included analysis of the interviews, the goal of which was to confirm the hypotheses \cite{seaman1999qualitative} that were formulated in the first phase. Both phases were performed iteratively, together with the data collection. This created the opportunity to improve the process of analysis as the study progressed, as well as, allowing the study to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase \cite{andersson2007spiral}.

%Grounded Theory
The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
%Codes
Each change identified in the spreadsheet was coded based on which module the change occurred in and two other characteristics: a) if the change added, removed or modified functionality, and b) if the change was a cosmetic change or not.
%Concepts
Grouping the codes by module allowed us to form general concepts of change. However, changes that affected the whole API were categorised on their own.
%Categories
These concepts were then grouped into categories based on common patterns between the concepts.
%Theory
These categories were then used to identify the most interesting trends in the evolution of the API. These trends were later used as a basis for discussion during the interview.

%RQ1
%We have all the changes and our suggested theories. Categorise them now
The categories identified previously were then classified according to the software maintenance categories \cite{chapin2001types}. The process used followed the decision tree used for the types of software evolution and software maintenance \cite{chapin2001types}. Each of the previously identified categories were given a main category of maintenance and a secondary category, if appropriate. This material was then used as a basis for answering \textbf{RQ1}.

@@

%Lehman's - RQ2
The analysis of the trends and the changes, combined with information gathered during the interview allowed us to answer \textbf{RQ2} by determining if Lehman's laws are applicable to the changes to the API \cite{lehman1980programs}.

%RQ1.1
The final stage of analysis was conducted once all the data had been analysed. To answer \textbf{RQ1.1}, we compared our analysis and interpretation of the change intents against the opinions expressed during the interview. Success was determined based on the amount of correct interpretations made about the intent behind the changes.
Our ability to correctly predict the motives compared to the actual motives of the designers which were made clear during the interviews, served as the basis for answering \textbf{RQ1.1}.
